Thread Pool in GeckoDB/BOLSTER

### 2018-07-12 Presentations/Milestone4/presentation.tex
Add presentation 4

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone III: Implementation \& evaluation setup}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

@@

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_queue.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\begin{itemize}
				\item Problem: waiting for a task to complete could lead to a
				race condition
				\item This was caused by the uncertainty of a thread\_task
				during transition between the priority queue and the
				thread pool
				\item Solution: slotmap with an atomic counter
			\end{itemize}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=1.0\textwidth]{waitingconcept.png}
		\end{column}
	\end{columns}
\end{frame}

>>>>

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone IV: Final presentation (wrap-up + evaluation results) }
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

@@

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_structure.png}
		Thread Pool System
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_queue.png}
		Enqueuing and Waiting for Tasks
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/thread_pool_use.png}
		Thread Pool Usage
	\end{center}
\end{frame}
